<!--
%\VignetteEngine{knitr}
%\VignetteIndexEntry{snpStatsWriter vignette}
-->

# snpStatsWriter

<font color="grey">
*Chris Wallace // [web](http://www-gene.cimr.cam.ac.uk/staff/wallace) // [email](mailto:chris.wallace at cimr.cam.ac.uk)*  
</font>


This is a package to write snpStats objects to disk in formats
suitable for reading by snphap, phase, mach, IMPUTE, beagle, and
(almost) anything else that expects a rectangular format.

We will load a small dataset included in the snpStats package

```{r}
library(snpStatsWriter)
data(testdata,package="snpStats")
A.small <- Autosomes[1:6,1:10]
nsnps <- ncol(A.small)
```

and write it to disk in lots of formats.

## snphap

```{r}
f <- tempfile()
write.snphap(A.small, file=f)
head(read.table(f,sep="\t"))
unlink(f)
```

## mach

```{r}
pf <- tempfile() ## pedigree file
mf <- tempfile() ## marker file
write.mach(A.small, a1=rep("1",nsnps), a2=rep("2",nsnps), pedfile=pf, mfile=mf)
head(read.table(mf))
head(read.table(pf))
unlink(pf)
unlink(mf)
```

## impute

```{r}
pf <- tempfile()
write.impute(A.small, a1=rep("1",nsnps), a2=rep("2",nsnps), bp=1:nsnps, pedfile=pf)
head(read.table(pf))
unlink(pf)
```

## beagle

```{r}
gf <- tempfile() ## genotype file
mf <- tempfile() ## marker file
write.beagle(A.small, a1=rep("1",nsnps), a2=rep("2",nsnps), bp=1:nsnps, gfile=gf, mfile=mf)
head(read.table(gf,header=TRUE))
head(read.table(mf))
unlink(gf)
unlink(mf)
```

## phase/fastPhase

NB phase input is a little different to most other formats!

```{r}
f <- tempfile()
write.phase(A.small, file=f)
head(scan(f,what=""))
unlink(f)
```
